Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-16 tensor/draft/draft-tensor-op.tex
[draft] Revise abstract and theory appendix

% \documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}
\documentclass[twocolumn,epjc3]{svjour3}

@@

%%
%% Comments
%%
\newcommand{\eos}[1]{{\color{red}{#1}}}   % things to be checked and replaced with EOS results
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\todo}[1]{{\color{magenta}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{brown}{ {\bf Checked: }{#1}}}}

@@

%
% useful variable for multiple same-size plots
%
\newlength{\relwidth}
%--------+---------+---------+---------+---------+---------+---------+---------+
%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+

@@

\begin{abstract}
  \todo{check}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
  e,\,\mu,\,\tau$) provides a lepton-forward-backward asymmetry,
  $A_{\rm FB}^\ell$, and a flat term, $F_H^\ell$, that are strongly
  suppressed in the standard model. In both, nonstandard tensor and
  scalar contributions are enhanced with respect to vector ones. We
  use latest experimental results for $\ell = \mu$ in combination with
  $B_s\to \bar\mu\mu$ to derive stronger model-independent constraints
  on tensor and scalar effective couplings and determine their impact
  on not-yet-measured angular observables in $B\to K^*\bar\mu\mu$,
  which feature the same suppression of vector couplings.  Most
  notably, the measurement of $F_H^\mu$ provides constraints on
  (pseudo-)scalar couplings and their chirality-flipped counterparts
  that are complementary to the ones from the branching ratio $B_s\to
  \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings. \fred{Try to shorten, add
    sentence ``independent of deviations in vector-coupling dominated
    observables''. There could be a bit of summary of outcome here, too}
  \todo{check captions of figures and tables}
\end{abstract}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgements}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  EOS \cite{EOS}. Concerning form factor results from lattice QCD, we thank
  Chris Bouchard and Matthew Wingate for communications on their results of
  $B\to K$ \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form
  factors. We thank also David Straub for his support with LCSR results of $B\to
  K^*$ form factors \cite{Straub:2015ica}.  C.B. was supported by the ERC
  Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the
  DFG Cluster of Excellence "Origin and Structure of the Universe". The
  computations have been carried out on the computing facilities of the
  Computational Center for Particle and Astrophysics (C2PAP).
\end{acknowledgements}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Theoretical Inputs
  \label{app:theory:inputs}
}

Here we describe the theoretical treatment of observables and collect numerical
input of the most relevant parameters. The software package {\tt EOS}
\cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for the calculation of
observables in $B_s\to \bar\mu\mu$ and $B\to K^{(*)}\bar\ell\ell$ and associated
constraints. Both the likelihood and the prior are defined entirely within EOS.

Concerning numerical input, we refer the reader to~\cite{Beaujean:2013soa} for
the compilation of nuisance parameters and according values, whose uncertainties
are negligible. Further, we adopt the same values for common nuisance parameters of
$i)$ the CKM quark-mixing matrix, $ii)$ the charm and bottom quark masses in the
$\overline{\rm MS}$ scheme, and $iii)$ the parameterisation of subleading corrections
in $1/m_b$ as given in \cite{Beaujean:2013soa}.

The updated prior of the $B_s$ decay constant $f_{B_s}$ enters the branching
ratio of $B_s\to \bar\mu\mu$. We adopt recent updates of the $N_f = (2 + 1)$
FLAG compilation \cite{Aoki:2013ldr}, see \reftab{tab:hadronic:nuisance}, which
averages the results of \cite{Bazavov:2011aa, McNeile:2011ng, Na:2012kp}.
More recent calculations with $N_f = (2+1+1)$ \cite{Dowdall:2013tga} and
$N_f = 2$ \cite{Carrasco:2013zta} are consistent with these averages.

The tensor and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ factorize naively,
i.e. they depend only on scalar and tensor $B\to K^{(*)}$ form factors. These amplitudes
are implemented in {\tt EOS} for $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ as
given in \cite{Bobeth:2007dw} and \cite{Bobeth:2012vn}, respectively and we refrain from
using respective form factor relations at large and low recoil for the tensor and scalar
$B\to K$ and $B\to K^*$ form factors.

\begin{table}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{cccc}
\hline
  Quantity & Prior & Unit & Reference\\
\hline \hline
  \multicolumn{4}{c}{$B_s$ decay constant}
\\
\hline
  $f_{B_s}$   &  $227.7 \pm 4.5$         &  MeV &  \cite{Aoki:2013ldr}\\
\hline \hline
  \multicolumn{4}{c}{$B\to K$ form factors}\\
\hline
  $f_+(0)$    &  $0.34 \pm 0.05$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $f_T(0)$    &  $0.38 \pm 0.06$         &  --    &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $b_1^0$     &  $-4.3^{+0.8}_{-0.9}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^+$     &  $-2.1^{+0.9}_{-1.6}$    &  --    &  \cite{Khodjamirian:2010vf}\\
  $b_1^T$     &  $-2.2^{+1.0}_{-2.0}$    &  --    &  \cite{Khodjamirian:2010vf}\\
\hline \hline
\multicolumn{4}{c}{$B\to K^*$ form factors}\\
\hline
\todo{fill in}\\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:hadronic:nuisance} Prior distributions of the nuisance parameters
   for hadronic quantities entering inclusive and exclusive decays. Note that
   $f_0(0) = f_+(0)$.
}
\end{center}
\end{table}

As we do not make use of form factor relations for tensor and scalar amplitudes
in $B\to K\bar\ell\ell$, additional nuisance parameters are included for the complete
set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
$z$-parameterization \cite{Khodjamirian:2010vf}, only five nuisance parameters
(listed in \reftab{tab:hadronic:nuisance}) arise due to the kinematic relation
$f_0(0) = f_+(0)$. As prior information, the LCSR results~\cite{Khodjamirian:2010vf}
and \cite{Ball:2004ye} have been averaged (see \reftab{tab:hadronic:nuisance} and
cf. \cite{Beaujean:2013soa}), and supplemented with lattice determinations~\cite{Bouchard:2013eph}.
Contrary to \cite{Beaujean:2013soa}, we do not adapt anymore a log-gamma prior for
the asymmetric uncertainties but rather a continuous, but asymmetric gaussian distribution.
The lattice results are given within a slightly different parameterisation necessitating
a conversion to the parameterisation used here. For this purpose, we generate the
form factors from the parameterisation \cite{Bouchard:2013eph}, including full
correlations, at three values of $q^2 = 17,\, 20,\, 23$ GeV$^2$ finding the results
compiled in \reftab{tab:btok-lattice}. (The $q^2$ values and number of points are chosen
such that the correlation of neighboring points does not exceed $80\%$.)
Subsequently, these ``data'' of the form factors is included in the likelihood
by means of a multivariate Gaussian in addition to experimental measurements.

@@

    \renewcommand{\arraystretch}{1.0}
    \caption{Mean values, uncertainties (top) and correlation
        information (bottom) of lattice points \cite{Bouchard:2013eph} for the
        $B\to K$ form factors $f_{0,+,T}(q^2)$.
        \label{tab:btok-lattice}
      }
\end{table*}

We change the parameterization of $B\to K^*$ form factors w.r.t. our previous
work \cite{Beaujean:2013soa} slightly and use now the simplified series expansion
(SSE) \cite{Bharucha:2010im}
\begin{align}
  \label{eq:SSE-FF-parameterization}
  F_i(q^2) & =
  \frac{1}{1 - q^2/M_{R,i}^2} \sum_k \alpha_k^i \left[z(q^2) - z(0)\right]^k \,,
\end{align}
with three parameters $\alpha_k^i$ ($k=0,1,2$) per form factor $i = V,\, A_{0,1},
T_{1,23}$ and two ($k=1,2$) for $i= A_{12}, T_2$. The parameters $\alpha_0^i$
correspond to $F_i(q^2 = 0)$ and the kinematic constraints
\begin{align}
  A_{12}(0) & = {\cal F}_{\rm kin}\, A_0(0) \,, &
  T_1(0) & = T_2(0)
\end{align}
are used to eliminate $\alpha_0^{A_{12}, T_2}$, where the kinematic factor
${\cal F}_{\rm kin} \equiv (M_B^2 - M_{K^*}^2)/(8 M_B M_{K^*})$ depends on the
$B$- and $K^*$-meson masses. The residual masses $M_{R,i}$ are set to the values
given in \cite{Straub:2015ica}.

This parameterization allows us to combine consistently available results
of form factors from different nonperturbative approaches, namely LCSR's at
large recoil and lattice at low recoil and implement simultaneously the
kinematic constraints. We determine the parameters $\alpha_i^k$
in a combined fit to form factor predictions of $V, A_{0,1,2},T_{1,2,3}$ from the
LCSR \cite{Straub:2015ica} and of $V, A_{0,1,12},T_{1,2,23}$ from the lattice
\cite{Horgan:2013hoa, Horgan:2015vla} calculations,
including their correlations. Further, we implement the second kinematic constraint
\begin{align}
  \label{eq:A12-constraint-q2max}
  A_{12}(q_{\rm max}^2) & = {\cal F}_{\rm kin}\, A_1(q_{\rm max}^2)
\end{align}
at maximal $q_{\rm max}^2 \equiv (M_B - M_{K^*})^2$. Uninformative flat priors
are chosen for all $\alpha_k^i$
\begin{align}
  \alpha_0^i & \in [0,\, 1] \,, &
  \alpha_{1}^i & \in [-2,\, 2]  \,, &
  \alpha_{2}^i & \in [-3,\, 3] \,.
\end{align}
The results of the LCSR predictions of the form factors have been provided to us
directly by the authors of \cite{Straub:2015ica} at $q^2 = (0.1,\, 4.1,\, 8.1,\,
12.1)\, \mbox{GeV}^2$ for $V,\, A_{0,1,12},\, T_{1,2,3}$, including their $28\times 28$
covariance matrix. \todo{In the case of lattice predictions, we proceed as in our
previous work \cite{Beaujean:2013soa} by generating form factor values of
$V,\, A_{0,1,12},\, T_{1,2,3}$ at $q^2 = (15,\, 19.21)\,\mbox{GeV}^2$ from updated results
\cite{Horgan:2015vla} (arXiv~v2), including their $8\times8$ correlation matrix
see \reftab{tab:btok-lattice}.}

\todo{We have compared our choice of three parameters in the SSE \refeq{eq:SSE-FF-parameterization}
versus two parameters only and found that in the latter case lattice form factor
results influence the fit such that form factors tend to be higher than LCSR
predictions at low $q^2$ leading to a worse fit. Hence we prefer the three-parameter
setup as it accommodates better LCSR and lattice results.}

@@

>>>>

\documentclass[twocolumn,epjc3]{svjour3}

@@

%%
%% Comments
%%
\newcommand{\fred}[1]{{\color{green}{#1}}}
\newcommand{\todo}[1]{{\color{magenta}{ {\bf ToDo: }{#1}}}}
\newcommand{\checked}[1]{{\color{brown}{ {\bf Checked: }{#1}}}}
\renewcommand{\checked}[1]{#1}

@@

%
% useful variable for multiple same-size plots
%
\newlength{\relwidth}

%
% codes
%
\def \eos{\texttt{EOS}}
%--------+---------+---------+---------+---------+---------+---------+---------+
%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+

@@

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  depends on two parameters, the lepton forward-backward asymmetry, $A_{\rm
    FB}^\ell$, and the flat term, $F_H^\ell$. Both are strongly suppressed in
  the standard model and constitute sensitive probes of tensor and scalar
  contributions. We use the latest experimental results for $\ell = \mu$ in
  combination with $B_s\to \bar\mu\mu$ to derive the strongest model-independent
  bounds on tensor and scalar effective couplings to date. The measurement of
  $F_H^\mu$ is complementary to that of the branching ratio of $B_s\to
  \bar\mu\mu$ and allows us---for the first time---to constrain all
  complex-valued (pseudo-)scalar couplings and their chirality-flipped
  counterparts in one fit. Based on Bayesian fits of various scenarios, we find
  that our bounds even become tighter when vector couplings are allowed to
  deviate from the standard model and that specific combinations of angular
  observables in $B \to K^*$ are still allowed to be up to two orders of
  magnitude larger than in the standard model, which would place them in the
  region of LHCb's sensitivity.
%   \todo{check captions of figures and tables}
\end{abstract}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgements}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  \eos~\cite{EOS}. Concerning form factor results from lattice QCD, we thank
  Chris Bouchard and Matthew Wingate for communications on their results of
  $B\to K$ \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form
  factors. We thank also David Straub for his support with LCSR results of $B\to
  K^*$ form factors \cite{Straub:2015ica}.  C.B. was supported by the ERC
  Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the
  DFG Cluster of Excellence "Origin and Structure of the Universe". The
  computations have been carried out on the computing facilities of the
  Computational Center for Particle and Astrophysics (C2PAP).
\end{acknowledgements}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  \checked{Theoretical Inputs}
  \label{app:theory:inputs}
}

Here we describe the theoretical treatment of observables and collect the
numerical input for the relevant parameters. The software package \eos{}
\cite{Bobeth:2011gi, Bobeth:2011nj, EOS} is used for the calculation of
observables in $B_s\to \bar\mu\mu$ and $B\to K^{(*)}\bar\ell\ell$ and associated
constraints. Both the likelihood and the prior are defined entirely within \eos.

Concerning numerical input, we refer the reader to~\cite{Beaujean:2013soa} for
the compilation of nuisance parameters relevant to this work. We adopt the same
values for fixed parameters and the same priors unless noted otherwise
below. Specifically, we use identical priors for for common nuisance parameters
of the CKM quark-mixing matrix, the charm and bottom quark masses in the
$\overline{\rm MS}$ scheme, and the parameterisation of subleading corrections
in $1/m_b$ as given in \cite{Beaujean:2013soa}.

The updated prior of the $B_s$ decay constant $f_{B_s}$ enters the branching
ratio of $B_s\to \bar\mu\mu$. We adopt recent updates of the $N_f = (2 + 1)$
FLAG compilation \cite{Aoki:2013ldr}, see \reftab{tab:hadronic:nuisance}, which
averages the results of \cite{Bazavov:2011aa, McNeile:2011ng, Na:2012kp}.  More
recent calculations with $N_f = (2+1+1)$ \cite{Dowdall:2013tga} and $N_f = 2$
\cite{Carrasco:2013zta} flavors are consistent with these averages.

The tensor and scalar amplitudes in $B\to K^{(*)} \bar\ell\ell$ factorize
naively, i.e. they depend only on scalar and tensor $B\to K^{(*)}$ form
factors. These amplitudes are implemented in \eos{} for $B\to K \bar\ell\ell$
and $B\to K^* \bar\ell\ell$ as given in \cite{Bobeth:2007dw} and
\cite{Bobeth:2012vn}, respectively and we refrain from using form-factor
relations at large and low recoil for the tensor and scalar $B\to K$ and $B\to
K^*$ form factors.  Therefore, we need additional nuisance parameters for the
complete set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
$z$ parameterization \cite{Khodjamirian:2010vf} and the kinematic relation
$f_0(0) = f_+(0)$, five nuisance parameters (listed in
\reftab{tab:hadronic:nuisance}) are needed. As prior information, we average the
LCSR results~\cite{Khodjamirian:2010vf} and \cite{Ball:2004ye} (see
\reftab{tab:hadronic:nuisance} and cf. \cite{Beaujean:2013soa}) supplement them
with lattice determinations~\cite{Bouchard:2013eph}.

Contrary to \cite{Beaujean:2013soa}, we do not choose a log-gamma distribution
for the asymmetric uncertainties in priors anymore but rather a continuous yet
asymmetric Gaussian distribution. In a unifying spirit, we now use the
continuous rather than discontinuous asymmetric Gaussian to approximate
asymmetric experimental intervals in our likelihood.

The lattice results are given in a slightly different parametrization
necessitating a conversion to the parametrization used here. For this purpose,
we generate the form factors from the parametrization
of~\cite{Bouchard:2013eph}, including full correlations, at three values of $q^2
= 17,\, 20,\, 23$ GeV$^2$.  Subsequently, these ``data'' are included in the
prior by means of a multivariate Gaussian whose mean and covariance is given in
\reftab{tab:btok-lattice}. The $q^2$ values and number of points are chosen such
that the correlation of neighboring points is small enough to keep the
covariance nonsingular.

\begin{table}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{cccc}
\hline
  Quantity & Prior & Reference\\
\hline
  \multicolumn{3}{c}{$B_s$ decay constant}
\\
\hline
  $f_{B_s}$   &  ($227.7 \pm 4.5$) MeV &  \cite{Aoki:2013ldr}\\
\hline
  \multicolumn{3}{c}{$B\to K$ form factors}\\
\hline
  $f_+(0)=f_0(0)$    &  $0.34 \pm 0.05$       &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $f_T(0)$    &  $0.38 \pm 0.06$      &  \cite{Khodjamirian:2010vf, Ball:2004ye}\\
  $b_1^0$     &  $-4.3^{+0.8}_{-0.9}$    &  \cite{Khodjamirian:2010vf}\\
  $b_1^+$     &  $-2.1^{+0.9}_{-1.6}$    &  \cite{Khodjamirian:2010vf}\\
  $b_1^T$     &  $-2.2^{+1.0}_{-2.0}$    &  \cite{Khodjamirian:2010vf}\\
\hline
\multicolumn{3}{c}{$B\to K^*$ form factors}\\
\hline
$\alpha_{0}^{A_0}$     & $0.35^{+0.02}_{-0.03}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{1}^{A_0}$     & $-1.21^{+0.08}_{-0.08}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{2}^{A_0}$     & $0.77^{+0.45}_{-0.48}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{0}^{A_1}$     & $0.2625^{+0.015}_{-0.015}$  & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{1}^{A_1}$     & $0.07^{+0.08}_{-0.08}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{2}^{A_1}$     & $0.045^{+0.12}_{-0.15}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{1}^{A_{12}}$  & $0.53^{+0.10}_{-0.14}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{2}^{A_{12}}$  & $0.32^{+0.33}_{-0.39}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{0}^{V}$       & $0.35^{+0.02}_{-0.03}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{1}^{V}$       & $-1.19^{+0.08}_{-0.08}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{2}^{V}$       & $1.55^{+0.33}_{-0.33}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{0}^{T_1}$     & $0.31^{+0.02}_{-0.02}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{1}^{T_1}$     & $-1.07^{+0.08}_{-0.08}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{2}^{T_1}$     & $1.40^{+0.30}_{-0.30}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{1}^{T_2}$     & $0.33^{+0.08}_{-0.10}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{2}^{T_2}$     & $0.26^{+0.21}_{-0.24}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{0}^{T_{23}}$  & $0.67^{+0.04}_{-0.05}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{1}^{T_{23}}$  & $0.93^{+0.28}_{-0.22}$     & \cite{Straub:2015ica, Horgan:2015vla}\\
$\alpha_{2}^{T_{23}}$  & $-0.15^{+0.86}_{-0.71}$      & \cite{Straub:2015ica, Horgan:2015vla}\\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:hadronic:nuisance} Prior distributions of the nuisance
  parameters for hadronic quantities. \checked{} }
\end{center}
\end{table}

@@

    \renewcommand{\arraystretch}{1.0}
    \caption{Mean values, standard deviations (top) and correlation
        coefficients (bottom) of lattice points \cite{Bouchard:2013eph} for the
        $B\to K$ form factors $f_{0,+,T}(q^2)$. \checked{}
        \label{tab:btok-lattice}
      }
\end{table*}

We change the parameterization of $B\to K^*$ form factors w.r.t. our previous
work \cite{Beaujean:2013soa} slightly and now use the simplified series
expansion (SSE) \cite{Bharucha:2010im}
\begin{align}
  \label{eq:SSE-FF-parameterization}
  F_i(q^2) & =
  \frac{1}{1 - q^2/M_{R,i}^2} \sum_k \alpha_k^i \left[z(q^2) - z(0)\right]^k \,,
\end{align}
with three parameters $\alpha_k^i$ ($k=0,1,2$) per form factor $i = V,\, A_0,A_1,
T_1,T_{23}$ and two ($k=1,2$) for $i= A_{12}, T_2$. The parameters $\alpha_0^i$
correspond to $F_i(q^2 = 0)$ and the kinematic constraints
\begin{align}
  A_{12}(0) & = {\cal F}_{\rm kin}\, A_0(0) \,, &
  T_1(0) & = T_2(0) \,,
\end{align}
are used to eliminate $\alpha_0^{A_{12}, T_2}$, where the kinematic factor
${\cal F}_{\rm kin} \equiv (M_B^2 - M_{K^*}^2)/(8 M_B M_{K^*})$ depends on the
$B$- and $K^*$-meson masses. The residual masses $M_{R,i}$ are set to the values
given in \cite{Straub:2015ica}.

This parameterization allows us to consistently combine available results of
form factors from different nonperturbative approaches, namely LCSR's at large
recoil and lattice at low recoil and to simultaneously implement the kinematic
constraints. We determine the parameters $\alpha_i^k$ in a combined fit to
form-factor predictions of $V, A_{0,1,2},T_{1,2,3}$ from the LCSR
\cite{Straub:2015ica} and of $V, A_0,A_1,A_{12},T_1,T_2,T_{23}$ from the lattice
\cite{Horgan:2013hoa, Horgan:2015vla} calculations, including their
correlations. We verified that the  constraint
\begin{align}
  \label{eq:A12-constraint-q2max}
  A_{12}(q_{\rm max}^2) & = {\cal F}_{\rm kin}\, A_1(q_{\rm max}^2)
\end{align}
at the kinematic endpoint $q_{\rm max}^2 \equiv (M_B - M_{K^*})^2$ is satisfied
to high accuracy by the above constraints and thus need not be imposed
explicitly. Uninformative flat priors are chosen for all $\alpha_k^i$ with
ranges
\begin{align}
  \alpha_0^i & \in [0,\, 1] \,, &
  \alpha_{1}^i & \in [-2,\, 2]  \,, &
  \alpha_{2}^i & \in [-3,\, 3] \,.
t\end{align}
The results of the LCSR form-factor predictions have been provided to us
directly by the authors of \cite{Straub:2015ica} at $q^2 = (0.1,\, 4.1,\, 8.1,\,
12.1)\, \mbox{GeV}^2$ for $V, A_0,A_1,A_{12},T_1,T_2,T_{3}$ including the
$28\times 28$ covariance matrix. Similar results could have been obtained by
``drawing'' form factors from the correlated parameters given in
\cite{Straub:2015ica} and ancillary files just as for $B \to K$ lattice form
factors.

But for the $B \to K^*$ lattice form factors this approach is not good enough as
we were not even able to select just two $q^2$ values and obtain a nonsingular
covariance. We then contacted the authors of~\cite{Horgan:2015vla} and obtained
the original values of the form factors (including correlation) at various
values in the interval $q^2 \in [11.9,\, 17.8]$ to which Horgan et al. fit the
SSE. The covariance has a block-diagonal structure with a 48$\times$48 block for
$V, A_0, A_1, A_{12}$ and a 36$\times$36 block for $T_1, T_2, T_{23}$. Having
the ``raw'' information on form-factor values is much more reliable and future
proof as there are no issues with artificial correlation and we could one day
decide to use yet another form-factor parametrization and fit it easily to these
data points.

We have compared the SSE fit \refeq{eq:SSE-FF-parameterization} with two versus
three parameters and found that in the former case lattice form factors
influence the fit such that form factors tend to be higher than LCSR predictions
at low $q^2$ leading to a poor fit. Hence we prefer the three-parameter setup as
it provides the flexibility needed to accomodate LCSR and lattice results. Means
and standard abbreviations of that three-parameter fit are given in
\reftab{tab:hadronic:nuisance}, we omit the correlations for the sake of brevity
but are happy to provide them.

@@

\todo{this is just filler text to avoid ``pdfendlink ended up in different
  nesting level than pdfstartlink’'' because entry \cite{Horgan:2013pva} is broken across two pages
}
